---
title: "About Me"
# image: 
sidebar: false
toc: false
---

<!-- See: https://twitter.com/thomas_mock/status/1563513015151996928 -->

## {{< fa graduation-cap >}} Education

<!-- TODO: template (include ?) for education and skills ? Or pure css ? Or table from R ? -->

- PhD in Cognitive Neurosciences (2017-2020) *[unfinished - COVID]*  
  [University of Rouen-Normandy]{.small style="color: lightgrey"}

- MSc in Cognitive Neurosciences (2015-2016)  
  [Grenoble INP]{.small style="color: lightgrey"}

- MSc in Organisational Psychology (2013-2015)  
  [University of Strasbourg]{.small style="color: lightgrey"}

## {{< fa location-dot >}} Location

Office U2.1.51, [LITIS Lab](https://litislab.fr/en/), Saint-Etienne-du-Rouvray, France.

<iframe src="https://www.google.com/maps/embed?pb=!1m14!1m8!1m3!1d2597.178095254828!2d1.068668!3d49.386623!3m2!1i1024!2i768!4f13.1!3m3!1m2!1s0x0%3A0x99721d01c683ed03!2sLitis!5e0!3m2!1sen!2sfr!4v1663157185844!5m2!1sen!2sfr" width="100%" height="450" style="border:0;" allowfullscreen="" loading="lazy" referrerpolicy="no-referrer-when-downgrade"></iframe>

## {{< fa gears >}} About this site

This website was made with [Quarto](https://quarto.org/) and R.

:::{.callout-tip collapse="true"}

# Expand for Session Info

```{r}
#| echo: false
#| output: false

source(here::here("src", "init.R"), echo = FALSE)
```

```{r}
#| echo: false

si <- sessioninfo::session_info(pkgs = "attached")

si$platform$Quarto <- system("quarto --version", intern = TRUE)

si$platform$pandoc <- strsplit(si$platform$pandoc, "@")[[1]][1]

si
```

:::