---
title: "{{< fa user-tie >}} About Me"
# image: 
title-block-banner: "#4B5B68"

sidebar: false
toc: false
---

## {{< fa graduation-cap >}} Education

- PhD in Cognitive Neurosciences (2017-2020)  
  [*Unfinished - COVID*]{.small style="color: #eac019"}  
  [University of Rouen-Normandy]{.small style="color: #888888"}

- MSc in Cognitive Neurosciences (2015-2016)  
  [Grenoble INP - Phelma]{.small style="color: #888888"}

- MSc in Organisational Psychology (2013-2015)  
  [University of Strasbourg]{.small style="color: #888888"}

## {{< fa address-book >}} Contact Me

You can send me an [email](mailto:marc.aurele.riviere+site@gmail.com) or directly message me on twitter at [@mariviere1](https://twitter.com/mariviere1)

## {{< fa location-dot >}} Location

Office U2.1.51, [LITIS Lab](https://litislab.fr/en/), Saint-Etienne-du-Rouvray, France.

<iframe src="https://www.google.com/maps/embed?pb=!1m14!1m8!1m3!1d2597.178095254828!2d1.068668!3d49.386623!3m2!1i1024!2i768!4f13.1!3m3!1m2!1s0x0%3A0x99721d01c683ed03!2sLitis!5e0!3m2!1sen!2sfr!4v1663157185844!5m2!1sen!2sfr" width="100%" height="450" style="border:0;" allowfullscreen="" loading="lazy" referrerpolicy="no-referrer-when-downgrade"></iframe>

## {{< fa code >}} About this site

This website was made with [Quarto](https://quarto.org/) and R.

:::{.callout-tip collapse="true"}

# Expand for Session Info

```{r}
#| echo: false
#| output: false

source(here::here("src", "init.R"), echo = FALSE)
```

```{r}
#| echo: false

si <- sessioninfo::session_info(pkgs = "attached")

si$platform$Quarto <- system("quarto --version", intern = TRUE)

si$platform$pandoc <- strsplit(si$platform$pandoc, "@")[[1]][1]

si
```

:::